%!TEX root = ../../../_main.tex
\subsection{Results in less and more specific cases}
\label{sec:sec:main-thesis-less-more-specific}

%\begin{exam}
%	Let $W = A_5$, $\theta = \id$ and $w = \ul s_1 \ul s_5 \ul s_3 \ul s_4 \ul s_2 \ul s_3$ as in Figure~\ref{fig:main-thesis-weakend-hypothesis-counterexample}. Denote the maximal element by $w_0$. Let $S_{12} = \{s_1,s_2\}$, $S_{23} = \{s_5,s_6\}$ and $S_{31} = \{s_1,s_5,s_6\}$. Then $w_0 \in wC_{S_i}$ for $i=1,2,3$ by $w_0 = w \ul s_2 \ul s_1 \ul s_2 = w \ul s_6 \ul s_5 \ul s_6 = w \ul s_6 \ul s_1 \ul s_5$, but $w_0 \notin wC_{S_{12} \cap S_{23} \cap S_{31}} = wC_{\emptyset} = \{w\}$.
%
%	\begin{figure}[ht]
%		\centering
%		\input{resources/tikz/main-thesis-weakend-hypothesis-counterexample}
%		\caption{Upper end of Hasse diagram of $Wk(A_5,\id)$}
%		\label{fig:main-thesis-weakend-hypothesis-counterexample}
%	\end{figure}
%\end{exam}

In this section we investigate some results and examples, in situations that are less or more specific than the situation from \ref{ques:main}.

\begin{exam}
	\typedlabel{exam:trivial-counterexample-for-arbitary-sets-of-generators}
	Let $W = A_3$ and $\theta$ be the Coxeter system autmorphism swapping $s_1$ and $s_3$ and let $w = s_1s_3 = s_3s_1$. We have $e \ul s_1 = s_3 s_1 = w = s_1 s_3 = e \ul s_3$. Hence $w \in eC_{\{s_1\}}$ and $w \in eC_{\{s_3\}}$ but $w \notin eC_{\{s_1\} \cap \{s_1\} \cap \{s_3\}} = eC_\emptyset = \{e\}$.
\end{exam}

Such a trivial counterexample like in \ref{exam:trivial-counterexample-for-arbitary-sets-of-generators} can not occur in the situation from \ref{ques:main}.

\begin{prop}
	Consider the situation from \ref{ques:main}. Let $w,v \in \ti{\theta}$ with $\rho(v) - \rho(w) = 1$ and let $v \in w C_{S_{ij}}$ for $1 \leq i < j \leq 3$. Then we have $v \in wC_T$.

	\begin{proof}
		By \ref{prop:no-triple-edges} there are at most two (not necessarily distinct) $s,t \in S$ with $w \ul s = v$ and $w \ul t = v$. Each set $S_{12},S_{23},S_{31}$ must at least contain $s$ or $t$, hence $s$ or $t$ is at least in two sets, say $s \in S_{12},S_{23}$. Hence $s \in S_1,S_2,S_3$ and therefore $v \in wC_T$.
	\end{proof}
\end{prop}

A hypothesis, that is much stronger than \ref{ques:main}, reads $wC_I \cap wC_J = wC_{I \cap J}$. If this would be true, \ref{ques:main} could be concluded immediately. Unfortunately it proves to be false. Again, double-edges yield a simple counterexample.

\begin{exam}
	\typedlabel{exam:cap-of-residuums}
	Let $w \in \ti{\theta}$ and $s,t$ two distinct generators with $w \ul s = w \ul t = v$. Then $wC_{\{s\}} \cap wC_{\{t\}} = \{w,v\} \neq \{w\} = wC_{\emptyset} = wC_{\{s\} \cap \{t\}}$.
\end{exam}

\begin{prop}
	\typedlabel{prop:s1-in-s2-main-special-case}
	Consider the situation from \ref{ques:main}. Suppose one set of $S_1,S_2,S_3$ is contained in another. Then
	$$ \forall \ 1 \leq i < j \leq 3 : v \in w C_{S_{ij}} \quad \Rightarrow \quad v \in w C_T. $$

	\begin{proof}
		Without loss of generality let $S_1 \subset S_2$. Then we have $S_{12} = S_1$. By this we get the identity
		$$ T = S_1 \cap S_2 \cap S_3 = S_{12} \cap S_3 = S_1 \cap S_3. $$
		Hence $v \in w C_T = w C_{S_{31}}$.
	\end{proof}
\end{prop}

\begin{lemm}
	Let $(W, S_1 \dot \cup S_2)$ be a reducible Coxeter system with $\ord(st) = 2$ for $s \in S_1, t \in S_2$. Let $\theta = \id$, $s_1,\ldots,s_m,s \in S_1$ and $t_1,\ldots,t_n,t \in S_2$. Then

	\begin{enumerate}
		\item $\ul s$ acts by twisted conjugation on $\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n$ if and only if it acts by twisted conjugation on $\ul s_1 \ldots \ul s_m$,
		\item $\ul t$ acts by twisted conjugation on $\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n$ if and only if it acts by twisted conjugation on $\ul t_1 \ldots \ul t_m$, and
		\item $\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n \ul s = \ul s_1 \ldots \ul s_m \ul s \ul t_1 \ldots \ul t_n$.
	\end{enumerate}

	\begin{proof}
		We have $\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n = t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n$ for some well chosen indices $1 \leq i_1 < \ldots < i_q \leq m$ and $1 \leq j_1 < \ldots < j_r \leq n$.

		\begin{enumerate}
			\item We prove this by a straight forward chain of equivalences.
			\begin{align*}
						& s (\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n) s  =  \ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n \\
				\iff	& s (t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n) s  =  t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n \\
				\iff	& (t_{i_q} \cdots t_{i_1} t_1 \cdots t_n) s s_{j_r} \cdots s_{j_1} s_1 \cdots s_m s  =  (t_{i_q} \cdots t_{i_1} t_1 \cdots t_n) s_{j_r} \cdots s_{j_1} s_1 \cdots s_m \\
				\iff	& s s_{j_r} \cdots s_{j_1} s_1 \cdots s_m s  =  s_{j_r} \cdots s_{j_1} s_1 \cdots s_m \\
				\iff	& s (\ul s_1 \ldots \ul s_m) s = \ul s_1 \ldots \ul s_m
			\end{align*}
			\item This part is almost the same as before.
			\begin{align*}
						& t (\ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n) t  =  \ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n \\
				\iff	& t (t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n) t  =  t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n \\
				\iff	& t t_{i_q} \cdots t_{i_1} t_1 \cdots t_n t (s_{j_r} \cdots s_{j_1} s_1 \cdots s_m)  =  t_{i_q} \cdots t_{i_1} t_1 \cdots t_n (s_{j_r} \cdots s_{j_1} s_1 \cdots s_m) \\
				\iff	& t t_{i_q} \cdots t_{i_1} t_1 \cdots t_n t  =  t_{i_q} \cdots t_{i_1} t_1 \cdots t_n \\
				\iff	& t (\ul t_1 \ldots \ul t_n) t = \ul t_1 \ldots \ul t_n
			\end{align*}
			Note that the last equivalence is not true in general. Suppose $v \in \ti{\theta}$ to be an arbitrary twisted expression. In general we cannot deduce the action of $\ul s$ on a subexpression of $v$ from the action of $\ul s$ on $v$ itself. But with the first part of this lemma we can first conclude, that $\ul t_1$ acts by twisted conjugation on $e$ if and only if it acts by twisted conjugation on $\ul s_1 \ldots \ul s_m$. Again with the same argument $\ul t_2$ acts by twisted conjugation on $\ul t_1$ iff it acts by twisted conjugation on $\ul s_1 \ldots \ul s_m \ul t_1$ and so forth.
			\item To avoid having to repeat the proof for twisted conjugative and multiplicative action of $\ul s$ we set $s' = s$ if $\ul s$ acts by twisted conjugation and else $s' = e$.
			\begin{align*}
					& \ul s_1 \ldots \ul s_m \ul t_1 \ldots \ul t_n \ul s \\
				= \	& s' (t_{i_q} \cdots t_{i_1} s_{j_r} \cdots s_{j_1} s_1 \cdots s_m t_1 \cdots t_n) s \\
				= \	& t_{i_q} \cdots t_{i_1} (s' s_{j_r} \cdots s_{j_1} s_1 \cdots s_m s) t_1 \cdots t_n \\
				= \	& t_{i_q} \cdots t_{i_1} (s_1 \ldots \ul s_m \ul s) t_1 \cdots t_n \\
				= \	& s_1 \ldots \ul s_m \ul s \ul t_1 \ldots \ul t_n
			\end{align*}
			Again note that the last to equalities need the two previous parts of this lemma. \qedhere
		\end{enumerate}
	\end{proof}
\end{lemm}