%!TEX root = ../../../_main.tex
\section{Application}
\label{sec:application}

This section is based on \cite{horn:kac-moody}.

\begin{defi}
	\typedlabel{defi:chamber-system}
	A \defword{chamber system over $I$} is a pair $\mathcal{C} = (C,(\sim_i, i \in I))$, with a nonempty set $C$, whose members are called \defword{chambers} and a family of equivalence relations $\sim_i$, indexed by $i \in I$, that satisfies the implication
	$$ c \sim_i d \wedge c \sim_j d \Rightarrow c = d \vee i = j $$
	for all $c,d \in C$ and $i,j \in I$. The cardinality $|I|$ is called the \defword{rank} of $\mathcal{C}$. If for two chambers $c,d$ we have $c \sim_i d$, then $c$ is called \defword{i-adjacent} to $d$ or just \defword{adjacent}.
\end{defi}

So the main assertion for chamber systems is, that two distinct chambers $c,d \in C$ are at most adjacent by one $i \in I$. For the rest of this paper $\mathcal{C} = (C,(\sim_i, i \in I))$ will always denote a chamber system and we will always assume, that chamber systems are of finite rank.

\begin{exam}
	For an arbitrary Coxeter system let $W$ act as set of chambers and for each generator $s \in S$ define a equivalence relation $w \sim_s v$ if and only if either $w = v$ or $ws = v$. That this are really equivalence relations is easy to check. So suppose $w \sim_s v$, $w \sim_t v$ for two distinct generators $s,t \in S$. The assumption $w \neq v$ immediately yields a contradiction by $ws = v = wt \iff s = t$. Hence this is indeed a chamber system.
\end{exam}

The previous example is just a special case of a quite general recipe to create chamber systems from groups, the so-called coset chamber systems.

\begin{defi}
	\theocite{Defnition 3.6.3}{buekenhout:diagram-geometry}
	Let $G$ be an arbitrary group with a subgroup $B$ and a family of subgroups $(G_i, i \in I)$ such that $B \subseteq G_i$ for $i \in I$. Choose the chamber set $C$ as the set of all $B$-cosets $gB$ for some $g \in G$ and define the equivalence relations $(\sim_i, i \in I)$ by $gB \sim_i hB$ iff $gG_i = hG_i$. Then we call this chamber system the \defword{coset chamber system} of $G$ on $B$ with respect to $(G_i, i \in I)$.
\end{defi}

\begin{lemm}
	Coset chamber systems are chamber systems.

	\begin{proof}
		As easy to check the $\sim_i$ are equivalence relations. So suppose $gB \sim_i hB$ and $gB \sim_j hB$ and let $gB \neq hB$, i.e. $h^{-1}g \notin B$. \todo \ Different definitions of chamber system at Horn and Buekenhout/Cohen?
	\end{proof}
\end{lemm}


If two chambers $c,d \in C$ in a chamber system are not adjacent, then there might be a chain of subsequent adjacent chambers with $c$ as first and $d$ as last chamber.

\begin{defi}
	Let $G = (c_0,\ldots,c_k)$ be a finite sequence of chambers $c_i \in C$ with $c_{i-1}$ adjacent to $c_i$ for all $1 \leq i \leq k$. Then $G$ is called a \defword{gallery} in $\mathcal{C}$ whereas the integer $k$ is called the \defword{length} of $G$. The first element $c_0$ of a gallery $G$ is denoted by $\alpha(G)$ and the last by $\omega(G)$. If for two chambers $c,d \in C$ there is a gallery $G$ with $\alpha(G) = c$ and $\omega(G) = d$, then we say that $G$ \defword{joins} $c$ and $d$. A gallery with G with $\alpha(G) = \omega(G)$ is called \defword{closed} and a gallery $G = (c_0,\ldots,c_k)$ with $c_{i-1} \neq c_i$ for all $1 \leq i \leq k$ is called \defword{simple}. If a gallery $G$ of length $k$ joins two chambers $c,d$ and there is no joining gallery of shorter length, then we call $G$ a \defword{minimal gallery joining $c$ and $d$}.
\end{defi}

Note, that two chambers are adjacent if and only if they can be joined by a gallery of length 1.

\begin{defi}
	The chamber system $\mathcal{C}$ is called \defword{connected} if any two chambers $c,d \in C$ can be joined by a gallery.
\end{defi}

\begin{defi}
	Let $G = (c_0,\ldots,c_k)$ be a gallery and let $J \subset I$ be a subset. If for $1 \leq i \leq k$ there is a $j \in J$ with $c_{i-1} \sim_j c_i$, then we call $G$ a \defword{$J$-gallery}. Two chambers $c,d \in C$, that have a $J$-gallery joining them, are called \defword{$J$-equivalent}, denoted by $c \sim_J d$.
\end{defi}

\begin{defi}
	For a chamber $c \in C$ and a subset $J \subseteq I$, we call the set $R_J(c) := \{ d \in C : c \sim_J d \}$ a \defword{$J$-residue}. If $|J| = 1$, say $J = \{i\}$, then $R_J(c) = R_{\{i\}}(c)$ is called a \defword{$i$-panel}.
\end{defi}

Note that for any chamber system $(C,(\sim_i, i \in I))$, $c \in C$ and $J \subseteq I$, the chamber system $(R_J(c), (\sim_j, j \in J))$ is connected by construction.

\begin{defi}
	Let $\mathcal{C}$ be a chamber system over $I$. We call it a \defword{residually connected} chamber system if the following holds: For every $J \subseteq I$ and every family of residues $(R_{I \setminus \{j\}}, j \in J)$ with pairwise nonempty intersection we have
	$$ \bigcap_{j \in J} R_{I \setminus \{j\}} = R_{I \setminus J}(c) $$
	for some $c \in C$.
\end{defi}

\begin{defi}
	A \defword{building} of type $(W,S)$ is a pair $(\mathcal{C}, \delta)$ with a nonempty set $\mathcal{C}$ and a map $\delta : \mathcal{C} \times \mathcal{C} \to W$, called \defword{distance function}, so that for $x,y \in \mathcal C$ and $w = \delta(x,y)$ we have
	\begin{axioms}
		\item[(Bu1)] $w = e \iff x = y$;
		\item[(Bu2)] for $z \in \mathcal C$ with $\delta(y,z) = s \in S$ we have $\delta(x,z) \in \{w,ws\}$, and if in addition $l(ws) = l(w) + 1$ then we have $\delta(x,z) = ws$;
		\item[(Bu3)] for $s \in S$ there exists a $z \in \mathcal C$ with $\delta(y,z) = s$ and $\delta(x,z) = ws$.
	\end{axioms}
\end{defi}

\begin{defi}
	Let $(\mathcal{C}, \delta)$ be building of type $(W,S)$. Then cardinality of $S$ is called the \defword{rank} of the building.
\end{defi}

\begin{defi}
	Let $(\mathcal{C}, \delta)$ be a building of type $(W,S)$. For each $s \in S$ we define $c,d \in C$ to be $s$-adjacent, if and only iff $\delta(c,d) \in \{e,s\}$. Then $(\mathcal{C}, (\sim_s, s \in S))$ is the to our building $(\mathcal{C}, \delta)$ \defword{associated chamber system}.
\end{defi}

Since 

\begin{lemm}
	Let $(\mathcal{C}, \delta)$ be a building of type $(W,S)$. Then the associated chamber system is a chamber system.

	\begin{proof}
		Let $c,d \in \mathcal{C}$ and $s,t \in S$ with $c \sim_s d$ and $c \sim_t d$. If $c \neq d$, then $\delta(c,d) = s$ and $\delta(c,d) = t$, hence $s = t$.
	\end{proof}
\end{lemm}

\begin{defi}
	A building $(\mathcal{C}, \delta)$ of type $(W,S)$ is called \defword{thick} (resp. \defword{thin}), if for every chamber $c \in \mathcal{C}$ and every $s \in S$ there are at least three (resp. exactly two) chambers $s$-adjacent to $c$.
\end{defi}

\begin{exam}
	\typedlabel{exam:thin-building}
	For a Coxeter system $(W,S)$ define a map
	$$ \delta_S : W \times W \to W : (x,y) \mapsto x^{-1}y. $$
	Then $\delta_S(x,y) = e \iff x = y$. Furthermore for $z \in W$ with $\delta_S(y,z) = s$, i.e. $z = ys$, we have $\delta_S(x,z) = x^{-1}z = x^{-1}ys = \delta(x,y)s$. For $s \in S$ and $x,y \in W$ choose $z = ys$. Then $\delta_S(y,z) = s$ and as before $\delta_S(x,z) = \delta_S(x,y)s$. Hence $(W,\delta_S)$ is a building of type $(W,S)$. More precisely, it is a thin building, since for every $s \in S$ and $x,y \in W$ we have $\delta_S(x,y) = x^{-1}y \in \{e,s\}$ if and only if $x = y$ or $y = xs$, hence there are excatly two chambers $s$-adjacent to $x$.
\end{exam}

This example for a thin building of type $(W,S)$ can be indeed called "the" thin building of type $(W,S)$ as the following lemma shows.

\begin{lemm}
	\theocite{Theorem 4.2.8}{buekenhout:diagram-geometry}
	Let $(\mathcal{C}, \delta)$ be a thin building of type $(W,S)$. Then it is isometric to the building $(W, \delta_S)$ (cf. \ref{exam:thin-building}).
\end{lemm}

\begin{defi}
	For a building $(\mathcal{C},\delta)$ of type $(W,S)$ we call a subset $\Sigma \subseteq \mathcal{C}$ an \defword{appartment}, if $(\Sigma, \delta|_\Sigma)$ is isometric to $(W,\delta_S)$ from \ref{exam:thin-building}, or equivalent if $(\sigma, \delta|_\Sigma)$ is thin.
\end{defi}

By the axioms of buildings, a building must have at least two chambers ($|S| \geq 1$ and $\mathcal{C} \neq \emptyset$). Hence by the next theorem we can think of thin buildings as the trivial ones for a given type $(W,S)$.

\begin{theo}
	\theocite{Theorem 11.2.5}{buekenhout:diagram-geometry}
	Let $(\mathcal{C},\delta)$ be a building. Then for any two chambers $c,d \in \mathcal{C}$ there is an appartment $\Sigma$ with $c,d \in \Sigma$. In particular every building contains at least one appartment.
\end{theo}

So thin buildings are precisely those, that contain excatly one apparment, i.e. are appartments themself.

\begin{defi}
	A building $(\mathcal{C},\delta)$ of type $(W,S)$ is called \defword{spherical} if $W$ is finite. In this case $W$ has a longest element $w_0$ and two chambers $c,d$ are called \defword{opposite}, if $\delta(c,d) = w_0$.
\end{defi}

\begin{defi}
	Let $(\mathcal{C},\delta)$ be a building of type $(W,S)$. A set of chambers $M \subseteq \mathcal{C}$ is called \defword{connected}, if any two chambers in $M$ can be joined by a gallery completeley contained in $M$. If in addition, every minimal gallery joining two chambers in $M$ is completeley contained in $M$, then $M$ is called \defword{convex}.
\end{defi}