\section{Residuums of rank 2}

\begin{defi}[One- and twosided operation]
	Let $(W,S)$ be a Coxeter system and $w \in W, s \in S$. If $w \ul s = \theta(s)ws$, then we say $s$ to operate twosided on $w$. Else we say $s$ to operate onesided on $w$.
\end{defi}

%TODO translate
\begin{defi}[Ein- und beidseitige endende Gesamtwirkung]
	Seien $(W,S)$ ein Coxetersystem, $w \in W$ und $s_1,\ldots,s_n \in S$. Falls $w \ul {s_1 \cdots s_n} = \theta(s_n)(w \ul {s_1 \cdots s_{n-1}}) s_n$ ist, so sagen wir, dass $s_1 \cdots s_n$ eine beidseitig endende Gesamtwirkung auf $w$ hat. Andernfalls sagen wir $s_1 \cdots s_n$ hat eine einseitig endende Gesamtwirkung auf $w$.
\end{defi}

\begin{defi}
	Let $(W,S)$ be a Coxeter system and $s,t \in S$ two distinct generators. We define:
	$$[st]^n :=
	\begin{cases}
	(st)^{\frac{n}{2}}, & n \textrm{ even} \\
	(st)^{\frac{n-1}{2}}s, & n \textrm{ odd} 
	\end{cases}$$
\end{defi}

%TODO translate
\begin{assu}
Seien $(W,S)$ ein Coxetersystem und $s,t \in S$ zwei verschiedene Erzeuger
von $W$. Dann gilt:
\begin{enumerate}
	\item \label{max-twocycle-length} Sei $m = \ord (st) < \infty$. Falls
	$w \ul{[st]^n} \neq w$ ist für alle $n \in \nn, n < 2m$, dann gilt $w \ul{(st)^{2m}} = w$.
	\item In $wC_{\{s,t\}}$ existieren keine drei Elemente derselben getwisteten Länge.
	\item Falls $s$ einseitig auf $w$ wirkt, dann gilt $w \ul{st} < w \ul{s}$ oder $w \ul{t} > w$.
	\item \label{twocycle-symmetry} Sei $w \ul{[st]^n} = w$ für ein $n \in
	\nn$. Dann ist $n$ gerade und es gilt eine der beiden folgenden Eigenschaften:
		\begin{enumerate}
			\item Für jedes $m \in \nn$ hat das Element $[st]^m$ genau dann eine
			beidseitig endende Gesamt\-wirkung auf $w$, wenn $[st]^{n/2+m}$ eine
			beidseitig endende Gesamtwirkung auf $w$ hat.
			\item Für jedes $m \in \nn$ hat das Element $[st]^m$ genau dann eine
			beidseitig endende Gesamt\-wirkung auf $w$, wenn $[st]^{n-m+1}$ eine
			beidseitig endende Gesamtwirkung auf $w$ hat.
		\end{enumerate}
\end{enumerate}
\end{assu}

\begin{lemm}
	\label{rank-2-residuums-are-convex} Let $(W,S)$ be a Coxeter system, $w \in W$ and $s,t \in S$ two distinct generators. Then $wC_{\{s,t\}}$ does not contain three elements of same twisted length.

	\begin{proof}
		Let $(W,S)$ be a Coxeter system, $w \in W$ with $\rank w = k$, $s, t \in S$ with $s \neq t$. Without loss of generality we can choose $w$ such that $w < w \ul s$ and $w < w \ul t$. Assume the existence of an element $u \in wC_{\{s,t\}}$ with $u \ul s < u$ and $u \ul t < u$. Then \cite[Lemma 3.8]{hultman:comb-twisted-invo} yields $s,t \in D_R(u)$. By using \cite[Lemma 3.9]{hultman:comb-twisted-invo} we conclude that $w \ul s \leq u$ and $w \ul t \leq u$. Hence there cannot exist more than two Elements of same twisted length.

		If no such $u$ exists, then $wC_{\{s,t\}} = w \ \dot \cup \ \{ w \ul{[st]^n} : n \in \nn \} \ \dot \cup \ \{ w \ul{[ts]^n} : n \in \nn \}$ and the assumption still holds.
	\end{proof}
\end{lemm}

\begin{lemm}
	\label{onesided-operations-only-at-top-or-bottom-end-of-twocycle}
	Let $(W,S)$ be a Coxeter system, $w \in S$ and $s,t \in S$ two distinct generators. If $s$ operates onesided on $w$ and $w \ul s < w$, then either $w \ul{st} < w \ul{s}$ or $w \ul{t} > w$.

	\begin{proof}
		We have $\theta(s)ws = w$ and $s \in D_R(w)$. If $t \notin D_R(w)$, then we are done. So suppose $t \in D_R(w)$. This means $w \ul s \leq w$ and $w \ul t \leq w$ and \cite[Lemma 3.9]{hultman:comb-twisted-invo} yields $w \ul {st} < w$ and $w \ul {ts} < w$. If $t \in D_R(w \ul s)$, then we are done. So suppose $t \notin D_R(w \ul s)$. Then $t \in D_R(w \ul {st})$. Together with $w \ul {st} \leq w$ \cite[Lemma 3.9(2)]{hultman:comb-twisted-invo} says $(w \ul {st}) \ul t \leq w \ul t$. Finally we get
		$$ ws = w \ul s = (w \ul {st}) \ul t \leq w \ul t = wt.$$
		Since $w \ul s$ and $w \ul t$ are of same twisted length they have to be equal and therefore $s = t$ which contradicts to our assumption of two distinct generators $s$ and $t$.
	\end{proof}
\end{lemm}