%!TEX root = ../../../_main.tex
\section{Affine and compact hyperbolic Coxeter groups}
\label{sec:coxeter-groups-affine-compact-hyperbolic}

Two other important classes of Coxeter systems are the so-called affine and compact hyperbolic ones. The affine ones arise from the finite ones by appending another generator in a certain manner. The compact hyperbolic seem quite exceptional, but we will see what makes them interesting soon.

\begin{defi}
	A irreducible Coxeter systems $(W,S)$ is called \defword{affine} if it is one of those from Figure~\ref{fig:affine-coxeter-systems}.
\end{defi}

\begin{defi}
	A irreducible Coxeter systems $(W,S)$ is called \defword{compact hyperbolic} if it is one of those from the Figures~\ref{fig:compact-hyperbolic-coxeter-systems-3},~\ref{fig:compact-hyperbolic-coxeter-systems-4} or \ref{fig:compact-hyperbolic-coxeter-systems-5}. In this paper the compact hyperbolic Coxeter systems are denoted with $X$, but note that this is not common in literature.
\end{defi}

For a less arbitrarily introduction of affine and compact hyperbolic Coxeter systems refer to \cite[Section 2.5, 6.7 -- 6.9]{humphreys:coxeter}. We use this approach, since we are only interested in them because of the following corollary and lemma.

\begin{coro}
	\typedlabel{coro:parabolic-subgroup-finite}
	Let $(W,S)$ be a affine or compact hyperbolic Coxeter system. Then every proper parabolic subgroup $W_{S'}$ with $S' \subsetneq S$ is either itself irreducible and finite or a direct product of irreducible finite Coxeter systems. In particular every proper parabolic subgroup is finite.

	\begin{proof}
		This is immediate by simple inspection. See Table~\ref{tab:parabolic-max-length} for a concrete list of all possible types of proper parabolic subgroups.
	\end{proof}
\end{coro}

\begin{lemm}
	The affine and compact hyperbolic Coxeter systems $(W,S)$ are precisely the ones, satisfying the following two conditions:
	\begin{enumerate}
		\item $(W,S)$ is infinite.
		\item $(W,S)$ is irreducible.
		\item For each $S' \subsetneq S$ the parabolic subgroup $W_{S'}$ is finite.
	\end{enumerate}

	\begin{proof}
		Obviously they are irreducible, by \ref{theo:irreducible-finit-coxeter-systems} they are infinite and by \ref{coro:parabolic-subgroup-finite} each proper parabolic subgroup is finite. For a proof that they are the only ones satisfying this see \cite{humphreys:coxeter}, \cite{chein:hyerbolic}.
	\end{proof}
\end{lemm}

\begin{figure}
	\centering
	\tikzstyle{vertex}=[draw,thick,circle,minimum size=2mm,inner sep=0pt]
	\tikzstyle{edge} = [draw,thick,-]
	\tikzstyle{weight} = [font=\small]

	\begin{tabular}{MMcMM}
	$\tilde A_1$
	&
	\tildeAone
	&
	\hspace*{\cgpadh}
	&
	$\tilde E_6$
	&
	\tildeEsix
	\\
	\vspace*{\cgpadv}
	\\
	$\tilde A_n$, {\tiny $n \geq 2$}
	&
	\tildeAn
	&
	\hspace*{\cgpadh}
	&
	$\tilde E_7$
	&
	\tildeEseven
	\\
	\vspace*{\cgpadv}
	\\
	$\tilde B_2 = \tilde C_2$
	&
	\tildeBCtwo
	&
	\hspace*{\cgpadh}
	&
	$\tilde E_8$
	&
	\tildeEeight
	\\
	\vspace*{\cgpadv}
	\\
	$\tilde B_n$, {\tiny $n \geq 3$}
	&
	\tildeBn
	&
	\hspace*{\cgpadh}
	&
	$\tilde F_4$
	&
	\tildeFfour
	\\
	\vspace*{\cgpadv}
	\\
	$\tilde C_n$, {\tiny $n \geq 3$}
	&
	\tildeCn
	&
	\hspace*{\cgpadh}
	&
	$\tilde G_2$
	&
	\tildeGtwo
	\\
	\vspace*{\cgpadv}
	\\
	$\tilde D_n$, {\tiny $n \geq 4$}
	&
	\tildeDn
	\end{tabular}
	\caption{All types of affine Coxeter systems}
	\label{fig:affine-coxeter-systems}
\end{figure}

\begin{figure}
	\centering
	\tikzstyle{vertex}=[draw,thick,circle,minimum size=2mm,inner sep=0pt]
	\tikzstyle{edge} = [draw,thick,-]
	\tikzstyle{weight} = [font=\small]

	\begin{tabular}{MMcMM}
		$X_3^1(p)$, {\tiny $7 \leq p < \infty$} & \comphyperthreeone \\ \vspace*{\cgpadv} \\
		$X_3^2(p,q)$, {\tiny $4 \leq p < \infty$, $5 \leq q < \infty$, $p \leq q$} & \comphyperthreetwo \\ \vspace*{\cgpadv} \\
		$X_3^3(p,q,r)$, {\tiny $3 \leq p,q < \infty$, $4 \leq r < \infty$, $p \leq q \leq r$} & \comphyperthreethree
	\end{tabular}
	\caption{All types of compact hyperbolic Coxeter systems of rank 3}
	\label{fig:compact-hyperbolic-coxeter-systems-3}
\end{figure}

\begin{figure}
	\centering
	\tikzstyle{vertex}=[draw,thick,circle,minimum size=2mm,inner sep=0pt]
	\tikzstyle{edge} = [draw,thick,-]
	\tikzstyle{weight} = [font=\small]

	\begin{tabular}{MMcMM}
		$X_4^1$ & \comphyperfourlineone & \hspace*{\cgpadh} & $X_4^5$ & \comphyperfoursquareone \\ \vspace*{\cgpadv} \\
		$X_4^2$ & \comphyperfourlinetwo & \hspace*{\cgpadh} & $X_4^6$ & \comphyperfoursquaretwo \\ \vspace*{\cgpadv} \\
		$X_4^3$ & \comphyperfourlinethree & \hspace*{\cgpadh} & $X_4^7$ & \comphyperfoursquarethree \\ \vspace*{\cgpadv} \\
		$X_4^4$ & \comphyperfourlinefour & \hspace*{\cgpadh} & $X_4^8$ & \comphyperfoursquarefour \\ \vspace*{\cgpadv} \\
		& & & $X_4^9$ & \comphyperfoursquarefive
	\end{tabular}
	\caption{All compact hyperbolic Coxeter systems of rank 4}
	\label{fig:compact-hyperbolic-coxeter-systems-4}
\end{figure}

\begin{figure}
	\centering
	\tikzstyle{vertex}=[draw,thick,circle,minimum size=2mm,inner sep=0pt]
	\tikzstyle{edge} = [draw,thick,-]
	\tikzstyle{weight} = [font=\small]

	\begin{tabular}{MMcMM}
		$X_5^1$ & \comphyperfiveone & \hspace*{\cgpadh} & $X_5^4$ & \comphyperfivefour \\ \vspace*{\cgpadv} \\
		$X_5^2$ & \comphyperfivetwo & \hspace*{\cgpadh} & $X_5^5$ & \comphyperfivefive \\ \vspace*{\cgpadv} \\
		$X_5^3$ & \comphyperfivethree
	\end{tabular}
	\caption{All compact hyperbolic Coxeter systems of rank 5}
	\label{fig:compact-hyperbolic-coxeter-systems-5}
\end{figure}